Measurement of dark matter halo concentrations using a bayesian approach

### 2014-05-21 paper/article.tex
writing formulas in the introduction

\section{Basics of the NFW profile}
\label{sec:basics}

The Navarro-Frenk-White mass profile can be normalized respect to the virial mass and written in function of the normalized radius respect to the virial radius $r=R/R_{vir}$ and the concentration $c$ 
\[
m_{nfw}\left(r;c\right)=A\left[\log\left(1+rc\right)-\left(\frac{rc}{rc+1}\right)\right]
\]
Where
\[
A=\left[\log\left(1+c\right)-\left(\frac{c}{c+1}\right)\right]^{-1} 
\]
\section{Bayesian Method}
\label{sec:method}

>>>>

\section{Basics of dark matter halos and the NFW profile}
\label{sec:basics}

The Navarro-Frenk-White density profile can be written as

\begin{equation}
\rho(r) = \frac{\rho_c\delta_c}{r/R_s(1+r/R_s)^2}, 
\end{equation}
%
where $\rho_c\equiv 3H^2/8\pi G$ is the Universe critical density,
$\delta_c$ is the halo dimensionless characteristic density. is a
normalization constant and $R_s$ is known as the scale radius, the
radius that marks the transition between the two power law behaviour
in the $\rho\propto r^{-1}$ for $r<R_s$ and $\rho\propto r^{-2}$ for
$r>R_s$.

One can define the scale radius as a fraction of the virial radius,
$R_{vir}$,

\begin{equation}
R_s = R_{vir}/c,
\end{equation}

where $c>1$ is known as the concentration of the halo.

Taking the virial radius as the radius that encloses 200 times the
critical density, the concentration and the characteristic density are
related by

\begin{equation}
\delta_c =\frac{200}{3}\frac{c^3}{[\ln(1+c)-c/(1+c)]}.
\end{equation}

Therefore, for a given value of the overdensity that defines a halo,
the density profile has only one free parameter: the concentration.

The total mass enclosed within a radius $r$ can be computed to be:

\begin{equation}
M(<r) = 4\pi\rho_c\delta_c  R_s^3\left[\ln \left
  (\frac{R_s+r}{r})\right) - \frac{r}{R_s+r}\right].
\end{equation}

If we now define dimensionless variables $x\equiv r/R_{\rm vir}$ and
$m\equiv M(<r)/M_{\rm vir}$...

profile can be normalized respect to the
virial mass and written in function of the normalized radius respect
to the virial radius $r=R/R_{vir}$ and the concentration $c$

\begin{equation}
m_{\rm NFW}\left(r;c\right)=A\left[\log\left(1+rc\right)-\left(\frac{rc}{rc+1}\right)\right) 
\end{equation}
Where
\begin{equation}
A=\left[\log\left(1+c\right)-\left(\frac{c}{c+1}\right)\right]^{-1} 
\end{equation}

\section{Bayesian Method}
\label{sec:method}
